An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-29 paper/1.introduction.tex
small change on the first paragraph of the introduction before boarding, and will revise the paper on the plane.

%In software, there are strong demands for synchronizing data. In database community this is known as ``the view update problem'' and researched for a long time.
% A Survey to View Update Problem 
%As a solution for this problem, bidirectional transformation (BX) is introduced.
The synchronization of data is a common problem. In the database community this problem is known as “the view update problem” and has been investigated for a long time~\cite{Bancilhon:1981:USR:319628.319634}. Bidirectional transformation (BX) is an approach to solve this problem.
As an example, let us consider a small BX program of $phead$\footnote{The actual program is shown in the next section.}. BX provides two functions: $get$ and $put$. Figure \ref{fig:eval-phead} denotes the behaviors of these functions when evaluating $phead$.

>>>>

%In software, there are strong demands for synchronizing data. In database community this is known as ``the view update problem'' and researched for a long time.
% A Survey to View Update Problem
%As a solution for this problem, bidirectional transformation (BX) is introduced.
The synchronization of data is a common problem. In the database community this problem is known as “the view update problem” and has been investigated for a long time~\cite{Bancilhon:1981:USR:319628.319634}. Bidirectional transformation (BX) provides a systematic approach to solving this problem.
As an example, consider a small BX program of $phead$\footnote{The actual program is shown in the next section.}, which consists of two functions: $get$ (for getting the head of an input list) and $put$ (for relfecting the output to the head of the input). Figure \ref{fig:eval-phead} shows the behaviors of these functions when evaluating $phead$.
